Counterfactual Training: Teaching Models Plausible and Actionable Explanations

### 2025-03-12 paper/preprint/paper.tex
vamos

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{plain}
\newtheorem{corollary}{Research Question}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\newcounter{quartocalloutnteno}
\newcommand{\quartocalloutnte}[1]{\refstepcounter{quartocalloutnteno}\label{#1}}

@@

\begin{tcolorbox}[enhanced jigsaw, titlerule=0mm, breakable, toptitle=1mm, rightrule=.15mm, leftrule=.75mm, colback=white, coltitle=black, left=2mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, opacitybacktitle=0.6, arc=.35mm, title={Note}, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, titlerule=0mm, breakable, toptitle=1mm, rightrule=.15mm, leftrule=.75mm, colback=white, coltitle=black, left=2mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, opacitybacktitle=0.6, arc=.35mm, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, titlerule=0mm, breakable, toptitle=1mm, rightrule=.15mm, leftrule=.75mm, colback=white, coltitle=black, left=2mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, opacitybacktitle=0.6, arc=.35mm, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, titlerule=0mm, breakable, toptitle=1mm, rightrule=.15mm, leftrule=.75mm, colback=white, coltitle=black, left=2mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, opacitybacktitle=0.6, arc=.35mm, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, titlerule=0mm, breakable, toptitle=1mm, rightrule=.15mm, leftrule=.75mm, colback=white, coltitle=black, left=2mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, opacitybacktitle=0.6, arc=.35mm, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, titlerule=0mm, breakable, toptitle=1mm, rightrule=.15mm, leftrule=.75mm, colback=white, coltitle=black, left=2mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, opacitybacktitle=0.6, arc=.35mm, title={Note \ref*{nte-train-final-run-train}: Training Phase}, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, titlerule=0mm, breakable, toptitle=1mm, rightrule=.15mm, leftrule=.75mm, colback=white, coltitle=black, left=2mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, opacitybacktitle=0.6, arc=.35mm, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0]

@@

Based on the findings from our initial large grid searches
(Section~\ref{sec-app-grid}), we tune selected hyperparameters for all
datasets: namely, the decision threshold \(\tau\) and the strength of
the energy regularization \(\lambda_{\text{reg}}\). The final
hyperparameter choices for each dataset are presented in \textbf{ADD
TABLE}. Detailed results for each data set are shown in
Figure~\ref{fig-tune-plaus-adult} to Figure~\ref{fig-tune-mat-over}.
From \textbf{ADD TABLE}, we notice that the same decision threshold of
\(\tau=0.5\) is optimal for all but on dataset. We attribute this to the
fact that a low decision threshold results in a higher share of mature
counterfactuals and hence more opportunities for the model to learn from
examples (Figure~\ref{fig-tune-mat-adult} to
Figure~\ref{fig-tune-mat-over}). This has played a role in particular
for our real-world tabular datasets and MNIST, which suffered from low
levels of maturity for higher decision thresholds. In cases where
maturity is not an issue, as for \emph{Moons}, higher decision
thresholds lead to better outcomes, which may have to do with the fact
that the resulting counterfactuals are more faithful to the model.
Concerning the regularization strength, we find somewhat high variation
across datasets. Most notably, we find that relatively low levels of
regularization are optimal for MNIST. We hypothesize that this finding
may be attributed to the uniform scaling of all input features (digits).
Finally, to increase the proportion of mature counterfactuals for some
datasets, we have also investigated the effect on the learning rate
\(\eta\) for the counterfactual search, but found little effect on the
results.

\begin{tcolorbox}[enhanced jigsaw, titlerule=0mm, breakable, toptitle=1mm, rightrule=.15mm, leftrule=.75mm, colback=white, coltitle=black, left=2mm, bottomtitle=1mm, colbacktitle=quarto-callout-warning-color!10!white, toprule=.15mm, opacitybacktitle=0.6, arc=.35mm, title={Package Version (Reproducibility)}, colframe=quarto-callout-warning-color-frame, bottomrule=.15mm, opacityback=0]

@@

\subsubsection{Key Parameters}\label{sec-app-tune}

@@

\begin{tcolorbox}[enhanced jigsaw, titlerule=0mm, breakable, toptitle=1mm, rightrule=.15mm, leftrule=.75mm, colback=white, coltitle=black, left=2mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, opacitybacktitle=0.6, arc=.35mm, title={Note \ref*{nte-tune-train}: Training Phase}, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, titlerule=0mm, breakable, toptitle=1mm, rightrule=.15mm, leftrule=.75mm, colback=white, coltitle=black, left=2mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, opacitybacktitle=0.6, arc=.35mm, title={Note \ref*{nte-tune-eval}: Evaluation Phase}, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacityback=0]

@@

>>>>

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{plain}
\newtheorem{corollary}{Research Question}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\newcounter{quartocalloutnteno}
\newcommand{\quartocalloutnte}[1]{\refstepcounter{quartocalloutnteno}\label{#1}}

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title={Note}, colbacktitle=quarto-callout-note-color!10!white, colback=white, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, rightrule=.15mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, left=2mm, titlerule=0mm, breakable, bottomrule=.15mm, leftrule=.75mm, toprule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, colbacktitle=quarto-callout-note-color!10!white, colback=white, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, rightrule=.15mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, left=2mm, titlerule=0mm, breakable, bottomrule=.15mm, leftrule=.75mm, toprule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, colbacktitle=quarto-callout-note-color!10!white, colback=white, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, rightrule=.15mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, left=2mm, titlerule=0mm, breakable, bottomrule=.15mm, leftrule=.75mm, toprule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, colbacktitle=quarto-callout-note-color!10!white, colback=white, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, rightrule=.15mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, left=2mm, titlerule=0mm, breakable, bottomrule=.15mm, leftrule=.75mm, toprule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, colbacktitle=quarto-callout-note-color!10!white, colback=white, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, rightrule=.15mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, left=2mm, titlerule=0mm, breakable, bottomrule=.15mm, leftrule=.75mm, toprule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title={Note \ref*{nte-train-final-run-train}: Training Phase}, colbacktitle=quarto-callout-note-color!10!white, colback=white, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, rightrule=.15mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, left=2mm, titlerule=0mm, breakable, bottomrule=.15mm, leftrule=.75mm, toprule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, colbacktitle=quarto-callout-note-color!10!white, colback=white, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, rightrule=.15mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, left=2mm, titlerule=0mm, breakable, bottomrule=.15mm, leftrule=.75mm, toprule=.15mm, opacityback=0]

@@

Based on the findings from our initial large grid searches
(Section~\ref{sec-app-grid}), we tune selected hyperparameters for all
datasets: namely, the decision threshold \(\tau\) and the strength of
the energy regularization \(\lambda_{\text{reg}}\). The final
hyperparameter choices for each dataset are presented in \textbf{ADD
TABLE}. Detailed results for each data set are shown in
Figure~\ref{fig-tune-plaus-adult} to Figure~\ref{fig-tune-mat-over}.
From \textbf{ADD TABLE}, we notice that the same decision threshold of
\(\tau=0.5\) is optimal for all but on dataset. We attribute this to the
fact that a low decision threshold results in a higher share of mature
counterfactuals and hence more opportunities for the model to learn from
examples (Figure~\ref{fig-tune-mat-adult} to
Figure~\ref{fig-tune-mat-over}). This has played a role in particular
for our real-world tabular datasets and MNIST, which suffered from low
levels of maturity for higher decision thresholds. In cases where
maturity is not an issue, as for \emph{Moons}, higher decision
thresholds lead to better outcomes, which may have to do with the fact
that the resulting counterfactuals are more faithful to the model.
Concerning the regularization strength, we find somewhat high variation
across datasets. Most notably, we find that relatively low levels of
regularization are optimal for MNIST. We hypothesize that this finding
may be attributed to the uniform scaling of all input features (digits).

Finally, to increase the proportion of mature counterfactuals for some
datasets, we have also investigated the effect on the learning rate
\(\eta\) for the counterfactual search and even smaller regularization
strengths for a fixed decision threshold of 0.5
(Figure~\ref{fig-tune_lr-plaus-adult} to
Figure~\ref{fig-tune_lr-plaus-over}). For the given low decision
threshold, we find that the learning rate has no discernable impact on
the proportion of mature counterfactuals
(Figure~\ref{fig-tune_lr-mat-adult} to
Figure~\ref{fig-tune_lr-mat-over}). We do notice, however, that the
results for MNIST are much improved when using a low value
\(\lambda_{\text{reg}}\), the strength for the engery regularization:
plausibility is increased by up to \textasciitilde10ppt
(Figure~\ref{fig-tune_lr-plaus-mnist}) and the proportion of mature
counterfactuals reaches 100\%.

One consideration worth exploring is to combine high decision thresholds
with high learning rates and low energy regularization strengths, which
we have not investigated here.

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title={Package Version (Reproducibility)}, colbacktitle=quarto-callout-warning-color!10!white, colback=white, colframe=quarto-callout-warning-color-frame, bottomtitle=1mm, rightrule=.15mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, left=2mm, titlerule=0mm, breakable, bottomrule=.15mm, leftrule=.75mm, toprule=.15mm, opacityback=0]

@@

\subsubsection{Key Parameters}\label{sec-app-tune-key}

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title={Note \ref*{nte-tune-train}: Training Phase}, colbacktitle=quarto-callout-note-color!10!white, colback=white, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, rightrule=.15mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, left=2mm, titlerule=0mm, breakable, bottomrule=.15mm, leftrule=.75mm, toprule=.15mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title={Note \ref*{nte-tune-eval}: Evaluation Phase}, colbacktitle=quarto-callout-note-color!10!white, colback=white, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, rightrule=.15mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, left=2mm, titlerule=0mm, breakable, bottomrule=.15mm, leftrule=.75mm, toprule=.15mm, opacityback=0]

@@

\subsubsection{Learning Rate}\label{sec-app-tune-lr}

The hyperparameter grid for tuning the learning rate is shown in
Note~\ref{nte-tune_lr-train}. The corresponding evaluation grid used for
these experiments is shown in Note~\ref{nte-tune_lr-eval}.

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title={Note \ref*{nte-tune_lr-train}: Training Phase}, colbacktitle=quarto-callout-note-color!10!white, colback=white, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, rightrule=.15mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, left=2mm, titlerule=0mm, breakable, bottomrule=.15mm, leftrule=.75mm, toprule=.15mm, opacityback=0]

\quartocalloutnte{nte-tune_lr-train}

  \begin{itemize}
  \tightlist
  \item
    Learning Rate: \texttt{0.1,\ 0.5,\ 1.0}
  \end{itemize}
\item
  Model: \texttt{mlp}
\item
  Training Parameters:

  \begin{itemize}
  \tightlist
  \item
    \(\lambda_{\text{reg}}\): \texttt{0.01,\ 0.1,\ 0.5}
  \item
    Objective: \texttt{full,\ vanilla}
  \end{itemize}
\end{itemize}

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title={Note \ref*{nte-tune_lr-eval}: Evaluation Phase}, colbacktitle=quarto-callout-note-color!10!white, colback=white, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, rightrule=.15mm, opacitybacktitle=0.6, toptitle=1mm, arc=.35mm, left=2mm, titlerule=0mm, breakable, bottomrule=.15mm, leftrule=.75mm, toprule=.15mm, opacityback=0]

\quartocalloutnte{nte-tune_lr-eval}

\paragraph{Plausibility}\label{plausibility-5}

The results with respect to the plausibility measure are shown in
Figure~\ref{fig-tune_lr-plaus-adult} to
Figure~\ref{fig-tune_lr-plaus-over}.

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/tune_lr/mlp/adult/evaluation/results/ce/lambda_energy_reg---lr_exper---lambda_energy_eval---lambda_energy_reg---lr_exper/plausibility_distance_from_target.png}}

\caption{\label{fig-tune_lr-plaus-adult}Average outcomes for the
plausibility measure across key hyperparameters. Data: Adult.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/tune_lr/mlp/credit/evaluation/results/ce/lambda_energy_reg---lr_exper---lambda_energy_eval---lambda_energy_reg---lr_exper/plausibility_distance_from_target.png}}

\caption{\label{fig-tune_lr-plaus-credit}Average outcomes for the
plausibility measure across key hyperparameters. Data: Credit.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/tune_lr/mlp/gmsc/evaluation/results/ce/lambda_energy_reg---lr_exper---lambda_energy_eval---lambda_energy_reg---lr_exper/plausibility_distance_from_target.png}}

\caption{\label{fig-tune_lr-plaus-gmsc}Average outcomes for the
plausibility measure across key hyperparameters. Data: GMSC.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/tune_lr/mlp/mnist/evaluation/results/ce/lambda_energy_reg---lr_exper---lambda_energy_eval---lambda_energy_reg---lr_exper/plausibility_distance_from_target.png}}

\caption{\label{fig-tune_lr-plaus-mnist}Average outcomes for the
plausibility measure across key hyperparameters. Data: MNIST.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/tune_lr/mlp/over/evaluation/results/ce/lambda_energy_reg---lr_exper---lambda_energy_eval---lambda_energy_reg---lr_exper/plausibility_distance_from_target.png}}

\caption{\label{fig-tune_lr-plaus-over}Average outcomes for the
plausibility measure across key hyperparameters. Data: Overlapping.}

\paragraph{Proportion of Mature CE}\label{proportion-of-mature-ce-1}

The results with respect to the proportion of mature counterfactuals in
each epoch are shown in Figure~\ref{fig-tune_lr-mat-adult} to
Figure~\ref{fig-tune_lr-mat-over}.

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/tune_lr/mlp/adult/evaluation/results/logs/objective---lr---lambda_energy_reg/percent_valid.png}}

\caption{\label{fig-tune_lr-mat-adult}Proportion of mature
counterfactuals in each epoch. Data: Adult.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/tune_lr/mlp/credit/evaluation/results/logs/objective---lr---lambda_energy_reg/percent_valid.png}}

\caption{\label{fig-tune_lr-mat-credit}Proportion of mature
counterfactuals in each epoch. Data: Credit.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/tune_lr/mlp/gmsc/evaluation/results/logs/objective---lr---lambda_energy_reg/percent_valid.png}}

\caption{\label{fig-tune_lr-mat-gmsc}Proportion of mature
counterfactuals in each epoch. Data: GMSC.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/tune_lr/mlp/mnist/evaluation/results/logs/objective---lr---lambda_energy_reg/percent_valid.png}}

\caption{\label{fig-tune_lr-mat-mnist}Proportion of mature
counterfactuals in each epoch. Data: MNIST.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/tune_lr/mlp/over/evaluation/results/logs/objective---lr---lambda_energy_reg/percent_valid.png}}

\caption{\label{fig-tune_lr-mat-over}Proportion of mature
counterfactuals in each epoch. Data: Overlapping.}
